SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-19 Chapters/sdm-autocorrelation.tex
SDM Minor change from previous commit.
SDM Autocorrelation theorems.

>>>>

\begin{lemma}
Let $r$ be the access radius given that $f$ percent of the hard locations are activated. Then, $\lim_{n \rightarrow \infty} r/n = 1/2$.
\label{thm:sdm-access-radius}
\end{lemma}
\begin{proof}

As the bits of the hard locations' addresses are randomly chosen, the distance between two hard locations follow a Binomial distribution with $n$ samples and probability 0.5 ($B(n, 0.5)$). For $n$ sufficiently large, the Binomial distribution can be approximated by a Normal distribution, i.e., $B(n, 0.5) \rightarrow \mathcal{N}(\mu = n/2, \sigma^2 = n/4)$.

Let $\Phi(x)$ be the cdf of the standard normal distribution. Let $z = \frac{r - n/2}{\sqrt{n}/2}$. Thus, $P(d(x, y) \le r) = \Phi(z)$. As $f = P(d(x, y) \le r)$, then, $f = \Phi(z)$.

Calculating the inverse, $z = \Phi^{-1}(f)$. Then,

\begin{align}
z &= \Phi^{-1}(f) \\
\frac{r - n/2}{\sqrt{n}/2} &= \Phi^{-1}(f) \\
r &= \frac{n}{2} + \Phi^{-1}(f) \frac{\sqrt{n}}{2} \\
\frac{r}{n} &= \frac{1}{2} + \Phi^{-1}(f) \frac{1}{2 \sqrt{n}}
\end{align}

Therefore, $n \rightarrow \infty \Rightarrow r/n \rightarrow 1/2$.
\end{proof}

\begin{theorem}
The autocorrelation vanishes when $n \rightarrow \infty$, i.e., $\lim_{n \rightarrow \infty} P(x_i = y_i | d(x, y) \le r) = 1/2$.
\label{thm:sdm-autocorrelation-convergence}
\end{theorem}
\begin{proof}

From Lemma \ref{thm:sdm-access-radius}, we know that $r = n/2$ for $n$ sufficiently large.

Suppose that $n$ is an even integer, then,

$$
\sum_{k=0}^{r} \binom{n}{k} = \sum_{k=0}^{n/2} \binom{n}{k} = \frac{1}{2} \sum_{k=0}^{n} \binom{n}{k} = \frac{2^n}{2} = 2^{n-1}
$$

And, also,

\begin{align*}
\sum_{k=0}^{r} \binom{n-1}{k} &= \sum_{k=0}^{n/2} \binom{n-1}{k} \\
    &= \frac{1}{2} \left[ \sum_{k=0}^{n-1} \binom{n-1}{k} - \binom{n-1}{n/2} \right] \\
    &= \frac{1}{2} \left[ 2^{n-1} - \binom{n-1}{n/2} \right] \\
    &= 2^{n-2} - \frac{1}{2} \binom{n-1}{n/2}
\end{align*}

\begin{align}
P(x_i = y_i | d(x, y) \le r) &= \frac{\sum_{k=0}^{r} \binom{n-1}{k}}{\sum_{k=0}^{r} \binom{n}{k}} \\
    &= \frac{2^{n-2} - \frac{1}{2} \binom{n-1}{n/2}}{2^{n-1}} \\
    &= \frac{2^{n-2}}{2^{n-1}} - \frac{1}{2^n} \binom{n-1}{n/2} \\
    &= \frac{1}{2} - \frac{1}{2^n} \binom{n-1}{n/2}
\end{align}

As $n \rightarrow \infty \Rightarrow \frac{1}{2^n} \binom{n-1}{n/2} \rightarrow 0$, the proof is done for $n$ even.

When $n$ is an odd integer, the steps of the proof are similar. Therefore, the proof is complete.

In Figure \ref{fig:sdm-10kbits-figure-7-3}, $n=10,000$ and we can notice that the autocorrelation has vanished as predicted by Theorem \ref{thm:sdm-autocorrelation-convergence}.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.75\textwidth]{./images02/sdm-10000bits-10000w-table-7-2.png}

  \caption{Given an address $x$ and a dimension $i$, how many hard locations with bitmatches in $i$ are activated by reading at $x$?  The histogram was obtained through numerical simulation. The red curve is the theoretical normal distribution found in Theorem \ref{T2}.}
  \label{fig:sdm-10kbits-figure-7-3}
\end{figure}
